---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# KFinReport

<!-- badges: start -->
[![R build status](https://github.com/mrobo2016/KFinReport/workflows/R-CMD-check/badge.svg)](https://github.com/mrobo2016/KFinReport/actions)
<!-- badges: end -->



Handling Korea's Corporate Filings from DART

This package utilizes Korea's Repository of Corporate Filings (DART).
It's goal is to assist users to browse through the repository via R. 
Users are able to retrieve corporate filings as data.
Upon retrieval, users can select the corporate of interest, the time span, types of report, etc. 


## Installation

You can install the released version of KFinReport from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("KFinReport")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mrobo2016/KFinReport")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(KFinReport)
ss <- report_earning1("22e453fa898ad0aafafec060ebc22dd916f2b3ff", "삼성전자", "2019" ,"y", "c" )
ss 
```
